\documentclass[12pt,a4paper]{article}
\usepackage{times}
\usepackage{durhampaper}
\usepackage{harvard}
\usepackage{graphicx}
\usepackage{float}
\usepackage{flafter}
\usepackage{nameref}
\usepackage[htt]{hyphenat}

\citationmode{abbr}
\bibliographystyle{agsm}

\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\title{Defeating MAC address randomisation: A hybrid, multi-layer approach for indoor location-based services}
\author{}
\student{Maximilian Grimmett}
\supervisor{Dr Eleni Akrida}
\degree{MEng Computer Science}

\newcommand{\absdiv}[1]{%
  \par\textbf{#1}\quad\ignorespaces \\
}

\date{}

\begin{document}

    \maketitle

    \begin{abstract}
        \absdiv{Context/Background}
        Recently, location-based indoor positioning services using 802.11 (Wi-Fi) have seen a rise in popularity of MAC randomisation to prevent tracking of individual devices throughout their stay.

        \absdiv{Aims}
        Primarily, this paper looks to implement a system that combines previous techniques for MAC \\ de-randomisation at different layers of the OSI model and conduct comparative research evaluating it relative to their individual use.
        Secondly, this paper looks to generalise these techniques to consider and evaluate groups of devices moving between different 802.11 nodes of the same network.
        Additionally, to enable such comparisons, this paper aims to produce a novel, modular testing and evaluation framework which uses Monte Carlo simulation to generate realistic, real-time data.
        
        \absdiv{Method}
        Due to the ethical implications of collecting potentially identifiable real-world data and the impracticality of doing so in a controlled environment, a real-world study is not suitable.
        While applicable real-world datasets do exist, they do not encompass all the fields required at the different levels of abstraction used by the proposed hybrid system.
        Instead, this paper proposes the use of Monte Carlo simulation of devices with and without MAC randomisation.

    \end{abstract}

    \begin{keywords}
        Location-based services, MAC randomisation, dynamic networks, privacy-preservation.
    \end{keywords}
    % \pagebreak

    \section{Introduction}\label{sec:introduction}
    \input{sections/00-introduction}
    % \pagebreak

    \section{Related Work}\label{sec:related-work}
    \input{sections/01-related-work}
    % \pagebreak

    \section{Solution}\label{sec:solution}
    \input{sections/02-solution}
    % \pagebreak

    \section{Validity}\label{sec:validity}
    \input{sections/03-validity}
    % \pagebreak

    \section{Results}\label{sec:results}
    \input{sections/04-results.tex}

    \section{Evaluation}\label{sec:evaluation}
    \input{sections/05-evaluation.tex}

    \section{Conclusion}\label{sec:conculsion}
    \input{sections/06-conclusion.tex}

    % \nocite{*}

    {\footnotesize
    \bibliography{projectpaper}}

\end{document}